Price of Anarchy for Mean Field Games

### 2018-07-30 PoA.tex
removed comments (Carmona preferred to remove comments when he uploaded to arXiv since you must upload the source as well)
made it clear that the limits come from the explicit solutions, not PDE literature

	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
	\begin{equation*}
		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation*}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$.

%	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing. Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
%	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large $r$.
	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u$, $D^{u,r}$, $D^{r \to \infty}_u> 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$ for $r \geq r^*$. Thus, we can deduce that for $r \geq r^*$, and for every $t \in [0,T]$:
	\begin{equation*}
	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }.
	\end{equation*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$. From the non-negativity of $u^r_t$, we have:
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
	Similarly, for every $t\in [0,T]$,
	$$\lim_{r\to \infty}w^r_t =: w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t =: \eta_t^{r\to \infty},$$
	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$. By the bounded convergence theorem we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{MFG,r})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{MFG,r\to \infty})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{MFG,r})^2 dt = 0.
	\end{equation*}

@@

	%\textbf{Case 1:} when
	From the assumption:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

@@

	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give for $b_2 \geq b_2^*$:
	\begin{equation*}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4}{c}\epsilon.
	\end{equation*}
	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $b_2$ and $\epsilon$, we conclude:
	\begin{equation*}
		\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0, 
	\end{equation*}
	and thus,
	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$
	%Todo: 
	%\textbf{Case 2}: when \begin{equation*}
	%\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq %\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
	%\end{equation*}
\end{proof}

@@

\begin{proof}
	% case when b2 bar \to infty
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0, \quad B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $t \in [0,T)$:
	\begin{equation*}
	\begin{array}{l}
	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t = (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2) w_t^{\bar{b}_2} = (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}

@@

	\textbf{Case 2: } When $\bar{b}_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		 \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}, \qquad 
		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u > 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.	
	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} -B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{\bar{b}_2 \to 0} = D^{\bar{b}_2 \to 0}_u,
	\label{eq:riccati_limiting_u}
	\end{equation}
	which we recall has an explicit solution. It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}. For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max\{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$ for all $\bar{b}_2 \leq \bar{b}^*_2$. Thus, for all $\bar{b}_2\leq \bar{b}^*_2$ and for every $t \in [0,T]$:
	\begin{equation*}
		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
	\end{equation*}

@@

	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	$$ 0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} <\infty.$$
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} > 1. $$
\end{proof}

@@

	% case 3: b1 to infinity
	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$. We have the following limits, for all $t \in [0,T)$:
	\begin{equation}
		\lim_{b_1 \to \infty} h_u(b_1,t) =  \lim_{b_1 \to \infty} h_w(b_1,t) = 2.
	\label{eq:ut_wt_lim_b1_infty}
	\end{equation}
	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and such that:
	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 3.$$

>>>>

	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
	\begin{equation*}
		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation*}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show directly from their explicit solutions that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$.

	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large $r$.
	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u$, $D^{u,r}$, $D^{r \to \infty}_u> 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$ for $r \geq r^*$. Thus, we can deduce that for $r \geq r^*$, and for every $t \in [0,T]$:
	\begin{equation*}
	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }.
	\end{equation*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$. From the non-negativity of $u^r_t$, we have:
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
	Similarly, for every $t\in [0,T]$,
	$$\lim_{r\to \infty}w^r_t =: w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t =: \eta_t^{r\to \infty},$$
	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$. By the bounded convergence theorem we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{MFG,r})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{MFG,r\to \infty})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{MFG,r})^2 dt = 0.
	\end{equation*}

@@

	From the assumption:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

@@

	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give for $b_2 \geq b_2^*$:
	\begin{equation*}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4}{c}\epsilon.
	\end{equation*}
	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $b_2$ and $\epsilon$, we conclude:
	\begin{equation*}
		\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0, 
	\end{equation*}
	and thus,
	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$
\end{proof}

@@

\begin{proof}
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0, \quad B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $t \in [0,T)$:
	\begin{equation*}
	\begin{array}{l}
	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t = (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2) w_t^{\bar{b}_2} = (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}

@@

	\textbf{Case 2: } When $\bar{b}_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		 \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}, \qquad 
		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u > 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.	
	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} -B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{\bar{b}_2 \to 0} = D^{\bar{b}_2 \to 0}_u,
	\label{eq:riccati_limiting_u}
	\end{equation}
	which we recall has an explicit solution. It is easy to show directly from the explicit solutions that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}. For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max\{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$ for all $\bar{b}_2 \leq \bar{b}^*_2$. Thus, for all $\bar{b}_2\leq \bar{b}^*_2$ and for every $t \in [0,T]$:
	\begin{equation*}
		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
	\end{equation*}

@@

	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. Clearly $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	$$ 0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} <\infty.$$
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} > 1. $$
\end{proof}

@@

	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$. We have the following limits, for all $t \in [0,T)$:
	\begin{equation}
		\lim_{b_1 \to \infty} h_u(b_1,t) =  \lim_{b_1 \to \infty} h_w(b_1,t) = 2.
	\label{eq:ut_wt_lim_b1_infty}
	\end{equation}
	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and such that:
	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 3.$$
